---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Welcome to StatAid

<!-- badges: start -->
<!-- badges: end -->

`hemRNA` is a free open-source software developed to help clinicians and biologists in analyzing RNAseq data. It has been designed to automatically process results in a standardized structure as provided by the associated script (RNAseq_main_script.sh).  

`hemRNA` has been developed with the R software, using the [Shiny package](https://shiny.rstudio.com/). [Golem](https://github.com/ThinkR-open/golem) has been used for package compilation and deployment.  


## Installation

You can install the development version from [GitHub](https://github.com/VincentAlcazer/hemRNA) either by cloning the repository or directly by downloading the package in R:

```{r Github install }

install.packages("remotes")
remotes::install_github("VincentAlcazer/hemRNA")

hemRNA::run_app()
```
